Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-25 paper/ijcai16.tex
paper: went through methods section, corrected errors and added fixmes

@@

\paragraph{Setting.} We assume to have a multi-attribute feature space $\calX$
of configurations $\vx = (x_1, \ldots, x_n)$ over $n$ features. For the time
being we will focus on binary features only, i.e. $x_z\in\{0,1\}$ for all
$z\in[n]$, to keep matters simple. This is a common choice for preference
elicitation methods~\cite{guo2010real,viappiani2010optimal}; discrete features
can be handled for instance by means of a simple one-hot encoding. Support for
linearly dependent continuous features will be discussed later on.

We further assume that the set of {\em feasible} configurations, denoted by
$\calX_\text{feasible}$, is expressed as
a conjunction of linear constraints. This is not a severe restriction:
arbitrary propositional constraints can be trivially encoded in this setting,
e.g. under the canonical mapping of $True$ to $1$ and $False$ to $0$, the
Boolean disjunction of two binary variables $x_1 \lor x_2$ can be rewritten as
$x_1 + x_2 \ge 1$.

@@

\paragraph{Non-linear Formulation.} We now introduce an initial formulation of
the optimization problem, that we do {\em not} aim at solving directly.

In the set-margin approach, the goal is twofold. First, for any given set size
$k\geq 1$, we want to find a {\em set} of $k$ weight vectors $\vw^{1}, \ldots,
\vw^{k}$, chosen so that all user-provided preferences are satisfied by the
largest possible margin (i.e. all weight vector are consistent with respect to
the user responses $\calD$, modulo inconsistencies) and so that they are
maximally diverse.  Second, we want to construct a {\em set} of $k$
configurations $\vx^{1}, \ldots, \vx^{k}$, so that each configuration $\vx^{i}$
is the ``best'' possible option when evaluated according to the corresponding
$\vw^{i}$, and consequently maximally diverse as well. These options will be
later employed to formulate the user queries.

The first goal achieved by translating all pairwise preferences $\calD$ into
ranking constraints: preferences of the form $\vy^h_+ \succ \vy^h_-$ become
linear inequalities of the form $\langle \vw^i, \vy^h_+ - \vy^h_- \rangle \geq
M$, where $M$ is the {\em margin} variable (which we aim at maximizing) and $h$
ranges over the responses.  Non-separable datasets, which occur in practice due
to user inconsistency, are handled by introducing slack variables (whose sum we
aim at minimizing). When augmented with the slacks, the above inequalities take
the form:
%
$$ \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h $$
%
where $\varepsilon^{i}_h$ is the penalty incurred by weight vector $\vw^{i}$
for violating the ranking of example $h$. Indifference preferences, i.e.
$\vy^h_1 \approx \vy^h_2$, are translated as $|\langle \vw^i, \vy^h_1 - \vy^h_2 \rangle| < \varepsilon^i_h$:
the slack increases with the difference between the estimated utility of the
two options.

Ideally, the second goal would be implemented as:
%
$$ \vx^{i} = \argmax_{\vx \in \calX_\text{feasible}} \langle \vw^{i}, \vx^{i} \rangle $$
%
However this formulation is highly impractical. We therefore only require 
each option $\vx^{i}$ to be the best {\em among} the configurations
$\{ \vx^i \}$. This can be accomplished by imposing
constraints of the form $\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq M$
for all $i,j\in[k]$, $i \ne j$.
This however does not guarantee that the produced $\{ \vx^{i} \}$ have a high
{\em absolute} utility. We therefore favor high-quality configurations by
introducing an additional term $\sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle$
in the objective function.

A straightforward encoding of the above desiderata leads to the following {\em
non-linear} optimization problem over the variables $M$, $\{ \vw^i \}$, $\{ \vx^i \}$:
%
{\footnotesize
\begin{align}
    \max
        & \;\; M - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h \label{eq:wyconstr}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \ge M \label{eq:wxconstr}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{i} \in \calX_{\text{feasible}} \label{eq:xbounds}
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{i} \ge 0 \nonumber
    \\
        & \;\; M \ge 0 \nonumber
\end{align}
}
%
Let us illustrate the above piece by piece. The objective is composed of four
parts: we maximize the shared margin $M$ (first part) and minimize the total
sum of the ranking errors $\veps^i$ incurred by each weight vector $\vw^{i}$
(second part), while at the same time regularizing the magnitude of the
weights (third part) and quality of the configurations $\{ \vx^{i} \}$ (last
part). The non-negative hyperparameters $\alpha,\beta,\gamma$ control the
influence of the various components.

The third part of the objective does require a more in depth explanation. In
many scenarios the user will have strong preferences about some attributes, but
will be indifferent to most of them~\cite{}. The $\ell_1$ penalty is frequently
used to improve the sparsity of learned models~\cite{}, with consequent gains
in generalization ability and efficiency, as confirmed by our empirical
findings (see Section~\ref{sec:experiments}). \stefano{add refs}

The two core constraints as Equations~\ref{eq:wyconstr} and \ref{eq:wxconstr},
which are taken directly from the discussion above. The former enforces the
correct ranking of the observed user preferences, while the latter ensures that
the generated configurations are ranked correctly with respect to the
corresponding weight vectors. Equations \ref{eq:wbounds} and \ref{eq:xbounds}
ensure that the weights and configurations are in fact feasible, while the
remaining two guarantee the non-negativity of the slack and margin variables.
Since we require $\vw^\bot \ge 0$, Eq.~\ref{eq:wbounds} also enforces the
weights to be non-negative.

Note that we are choosing the options $\{ \vx^i \}$ and the weight vectors $\{
\vw^i \}$ {\em simultaneously}. Since we maximize the margin $M$, the optimizer
will prefer a set of outcomes $\{ \vx^{i} \}$ that partition the weight space
roughly equally, and corresponding utility functions such that each $\vw^{i}$
lies (intuitively) close to the centre of each subregion. See
Figure~\ref{fig:setmargin} for a depiction of this intuition.

@@

\paragraph{MILP Formulation.} This initial formulation is problematic, as
Eq~\ref{eq:wxconstr} involves quadratic terms. Here we show how to reformulate
the problem as a mixed integer linear program (MILP). Our goal is to replace
Eq~\ref{eq:wxconstr} with a set of linear constraints through a suitable
variable transformation.

In order to do so, we introduce a set of fresh variables $p^{i,j}_z$ for every
$i,j\in[k]$ and $z\in[n]$. Assuming for the time being that the new variables
do satisfy the equation $p^{i,j}_z = w^i_z x^i_z$, we rewrite the fourth
component of the objective function in terms of the new variables as:
%
$$ \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z $$
%
and, similarly, Eq~\ref{eq:wxconstr} as:
%
\[ \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M \label{eq:pxconstr} \]
%
The fact that $p^{i,j}_z = w^{i}_z x^{i}_z$ is achieved by
setting the following additional constraints. We distinguish between two cases:
(i) $p^{i,i}_z$, and (ii) $p^{i,j}_z$ for $i \ne j$.  Recall that we are
maximizing the margin $M$. Now, due to Eq~\ref{eq:pxconstr}, the optimizer will
try to keep $p^{i,i}_z$ as large as possible and $p^{i,j}_z$ as small as
possible.

@@

(Case ii) We add an explicit lower bound:
%
$$ p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \} $$
%
If $x^i_z = 1$ the lower bound simplifies to $\max \{ 0, w^{i}_z \} = w^{i}_z$,
due to the non-negativity of $w^i_z$. Otherwise, if $x^i_z = 0$
then the lower bound becomes $\max \{ 0, w^{i}_z - w_\text{max} \}$, where
the second term is at most $0$. Since $p^{i,j}_z$ is being minimized, in both
cases it will attain the lower bound, and thus satisfy $p^{i,j}_z = w^i_z
x^i_z$\footnote{Since $M$ is upper-bounded by Eq.~\ref{eq:wyconstr}, in some
cases the $p^{i,j}_z$ variables do not attain the lower bound. As a
consequence, the MILP reformulation of Eq.~\ref{eq:wxconstr} is marginally
inexact. Despite this issue, the MILP formulation acceptably in practice.}.

Substituting the above MILP constraints into the original non-linear
formulation, we obtain the following mixed-integer linear problem:
%
{\footnotesize
\begin{align}
    \max
        & \;\; M - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h \nonumber
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M
    \\
        & \;\; \forall \; i \in [k], \forall \; z \in [n] \nonumber
    \\
        & \;\; \qquad p^{i,i}_z \le \min \{ w_\text{max} x^{i}_z, w^{i}_z \}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \nonumber
    \\
        & \;\; \qquad p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds2}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{i} \in \calX_{\text{feasible}} \nonumber
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{i}_h \ge 0 \nonumber
    \\
        & \;\; M \ge 0 \nonumber
\end{align}
}
%
which can be solved by any suitable MILP solver.

\paragraph{Set-wise max-margin.} The full {\sc SetMargin} algorithm follows the
usual preference elicitation loop. Starting from an initially empty set of user
responses $\calD$, it repeatedly solves the MILP problem above using the set
$\calD$ to enforce ranking constraints on the weight vectors $\{\vw^i\}$. The
generated configurations $\{\vx^i\}$, which are chosen to be as good as
possible with respect to the estimated user preferences, and as diverse as
possible, are then employed to formulate a set of user queries. The new replies
are added to $\calD$ and the whole procedure is repeated. The algorithm
terminates after a fixed number of iterations, or once another suitable
condition is met. The procedure is sketched in Algorithm~\ref{alg:setmargin}.

@@

@@

First, we rewrite the weight vector as $\vw = (\vw_B;\vw_R)$. The utility
becomes:
%
$$ \langle \vw, \vx \rangle = \langle \vw_B, \vx_B \rangle + \langle \vw_R, C \vx_B \rangle = \langle \vw_B + C^\top \vw_B, \vx_B \rangle $$
%
The generalized problem is obtained by substituting $\vw^i$ with $\vv^i := \vw_B^i + C^\top \vv_B^i$ and $p^{i,j}_z$
with $q^{i,j}_z := (\vw^i_B + C^\top \vw^i_R)_z x^j_z$ in the MILP problem.
All constraints remain the same, except Eq.~\ref{eq:wbounds2}, which must be
rewritten in terms of $\vv^i$:
%
$$ \forall \; i \in [k] \;.\; (\vw_B^\bot + C^\bot \vw_R) \le \vv^i \le (\vw_B^\top + C^\top \vw_R^\top)$$
%
As can be seen, non-negativity of $C$ is required for the weights $\{\vv^i\}$
to be non-negative.

>>>>

\andrea{manca un titolo a questa sezione?}

@@

\paragraph{Setting.} We assume to have a multi-attribute feature space $\calX$
of configurations $\vx = (x_1, \ldots, x_n)$ over $n$ features. For the time
being we will focus on binary features only, i.e. $x_z\in\{0,1\}$ for all
$z\in[n]$, to keep matters simple. This is a common choice for preference
elicitation methods~\cite{guo2010real,viappiani2010optimal}; discrete features
can be handled for instance by means of a simple one-hot encoding. Support for
linearly dependent continuous features will be discussed later on. 
\andrea{mmh sembra che gestiamo solo booleani.. riscriverei che ci concentriamo solo su feature categoriche, e 
che le rappresentiamo con one-hot encoding come tipico dei metodi preference elicitation..}

We further assume that the set of {\em feasible} configurations, denoted by
$\calX_\text{feasible}$, is expressed as
a conjunction of linear constraints. This is not a severe restriction:
arbitrary propositional constraints can be trivially encoded in this setting,
e.g. under the canonical mapping of $True$ to $1$ and $False$ to $0$, the
Boolean disjunction of two binary variables $x_1 \lor x_2$ can be rewritten as
$x_1 + x_2 \ge 1$. \andrea{mmh cosa ci da in piu'? altrimenti non e' una restrizione ma un modo 
per scrivere vincoli logici}

@@

\paragraph{Non-linear Formulation.} We first introduce the problem
formulation as a mixed integer non-linear optimization problem, and
then show how to reduce it to a mixed integer linear optimization one.

The goal of our setwise max-margin approach is twofold. First, for any
given set size $k\geq 1$, we want to find a {\em set} of $k$ weight
vectors $\vw^{1}, \ldots, \vw^{k}$, chosen so that all user-provided
preferences are satisfied by the largest possible margin (i.e. all
weight vectors are consistent with respect to the user responses
$\calD$, modulo inconsistencies) and so that they are maximally
diverse.  Second, we want to construct a {\em set} of $k$
configurations $\vx^{1}, \ldots, \vx^{k}$, so that each configuration
$\vx^{i}$ is the ``best'' possible option when evaluated according to
the corresponding $\vw^{i}$ and configurations are maximally diverse
among each other. These options will be later employed to formulate
the user queries.

The first goal is achieved by translating all pairwise preferences
$\calD$ into ranking constraints: preferences of the form
$\vy^h_+ \succ \vy^h_-$ become linear inequalities of the form
$\langle \vw^i, \vy^h_+ - \vy^h_- \rangle \geq M$, where $M$ is the
{\em margin} variable (which we aim at maximizing) and $h$ ranges over
the responses.  Non-separable datasets, which occur in practice due to
occasional inconsistencies in user feedback, are handled by
introducing slack variables (whose sum we aim at minimizing). When
augmented with the slacks, the above inequalities take the form:
%
$$ \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h $$
%
where $\varepsilon^{i}_h$ is the penalty incurred by weight vector $\vw^{i}$
for violating the margin separation of pair $h$. Indifference preferences, i.e.
$\vy^h_1 \approx \vy^h_2$, are translated as $|\langle \vw^i, \vy^h_1 - \vy^h_2 \rangle| < \varepsilon^i_h$;
the slack increases with the difference between the estimated utility of the
two options.

The second goal requires to jointly maximize the utility of each
$\vx^{i}$ according to its corresponding weight vector $\vw^i$ and its
scoring difference with respect to the other configurations $\vx^j$ in
the set. We achieve this by maximizing the sum of utilities
$\sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle$ and adding ranking
constraints of the form
$\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq M$ for all
$i,j\in[k]$, $i \ne j$.

% Ideally, the second goal would be implemented as:
% %
% $$ \vx^{i} = \argmax_{\vx \in \calX_\text{feasible}} \langle \vw^{i}, \vx^{i} \rangle $$
% %
% However this formulation is highly impractical. We therefore only require 
% each option $\vx^{i}$ to be the best {\em among} the configurations
% $\{ \vx^i \}$. This can be accomplished by imposing
% constraints of the form $\langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \geq M$
% for all $i,j\in[k]$, $i \ne j$.
% This however does not guarantee that the produced $\{ \vx^{i} \}$ have a high
% {\em absolute} utility. We therefore favor high-quality configurations by
% introducing an additional term $\sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle$
% in the objective function.

A straightforward encoding of the above desiderata leads to the
following mixed integer {\em non-linear} optimization problem over the
variables $M$, $\{ \vw^i \}$, $\{ \vx^i \}$: \andrea{dovremmo forse specificare i domini delle variabili per chiarire la natura mixed}
%
{\footnotesize
\begin{align}
    \max
        & \;\; M - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \langle \vw^{i}, \vx^{i} \rangle
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h \label{eq:wyconstr}
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \langle \vw^{i}, \vx^{i} - \vx^{j} \rangle \ge M \label{eq:wxconstr}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{i} \in \calX_{\text{feasible}} \label{eq:xbounds}
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{i} \ge 0 \nonumber
    \\
        & \;\; M \ge 0 \nonumber
\end{align}
} \andrea{perche' un punto tra il quantificatore e la formula? inoltre mi sa che ``n'' e' usato per due cose, queries e features}
%
Let us illustrate the above piece by piece. The objective is composed of four
parts: we maximize the shared margin $M$ (first part) and minimize the total
sum of the ranking errors $\veps^i$ incurred by each weight vector $\vw^{i}$
(second part), while at the same time regularizing the magnitude of the
weights (third part) and the quality of the configurations $\{ \vx^{i} \}$ (last
part). The non-negative hyperparameters $\alpha,\beta,\gamma$ control the
influence of the various components.

The third part of the objective does require a more in depth explanation. In
many scenarios the user will have strong preferences about some attributes, but
will be indifferent to most of them~\cite{}. The $\ell_1$ penalty is frequently
used to improve the sparsity of learned models~\cite{lasso}, with consequent gains
in generalization ability and efficiency, as confirmed by our empirical
findings (see Section~\ref{sec:experiments}). \stefano{add refs}

The two core constraints are Equations~(\ref{eq:wyconstr}) and~(\ref{eq:wxconstr}),
which are taken directly from the discussion above. The former enforces the
correct ranking of the observed user preferences, while the latter ensures that
the generated configurations are diverse in terms of the weight vectors they
maximize. Equations~(\ref{eq:wbounds}) and~(\ref{eq:xbounds})
ensure that the weights and configurations are in fact feasible, while the
remaining two guarantee the non-negativity of the slack and margin variables.
Since we require $\vw^\bot \ge 0$, Eq.~(\ref{eq:wbounds}) also enforces the
weights to be non-negative.

Note that we are choosing the configurations $\{ \vx^i \}$ and the weight vectors $\{
\vw^i \}$ {\em simultaneously}. Since we maximize the margin $M$, the optimizer
will prefer a set of configurations $\{ \vx^{i} \}$ that partitions the weight space
roughly equally, and corresponding utility functions such that each $\vw^{i}$
lies (intuitively) close to the centre of each subregion. See
Figure~\ref{fig:setmargin} for a depiction of this intuition.\andrea{mmh non chiarissimo, da rivedere insieme, legenda inclusa}

@@

\paragraph{MILP Formulation.} This initial formulation is problematic,
as Eq.~(\ref{eq:wxconstr}) involves quadratic terms over mixed
continuous integer variables.\andrea{check} Here we show how to reformulate the
problem as a mixed integer linear program (MILP). Our goal is to
replace Eq.~(\ref{eq:wxconstr}) with a set of linear constraints through
a suitable variable transformation.

In order to do so, we introduce a set of fresh variables $p^{i,j}_z$ for every
$i,j\in[k]$ and $z\in[n]$. Assuming for the time being that the new variables
do satisfy the equation $p^{i,j}_z = w^i_z x^j_z$, we rewrite the fourth
component of the objective function in terms of the new variables as:
%
$$ \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z $$
%
and, similarly, Eq.~(\ref{eq:wxconstr}) as:
%
\[ \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M \label{eq:pxconstr} \]
%
The fact that $p^{i,j}_z = w^{i}_z x^{j}_z$ is achieved by
setting the following additional constraints. We distinguish between two cases:
(i) $p^{i,i}_z$ and (ii) $p^{i,j}_z$ for $i \ne j$.  Recall that we are
maximizing the margin $M$. Now, due to Eq.~(\ref{eq:pxconstr}), the optimizer will
try to keep $p^{i,i}_z$ as large as possible and $p^{i,j}_z$ as small as
possible.

@@

(Case ii) We add an explicit lower bound:
%
$$ p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \} $$
%
If $x^j_z = 1$ the lower bound simplifies to $\max \{ 0, w^{i}_z \} = w^{i}_z$,
due to the non-negativity of $w^i_z$. Otherwise, if $x^j_z = 0$
then the lower bound becomes $\max \{ 0, w^{i}_z - w_\text{max} \}$, where
the second term is at most $0$. Since $p^{i,j}_z$ is being minimized, in both
cases it will attain the lower bound, and thus satisfy $p^{i,j}_z = w^i_z
x^j_z$.\footnote{Since $M$ is upper-bounded by Eq.~(\ref{eq:wyconstr}), in some
cases the $p^{i,j}_z$ variables do not attain the lower bound. As a
consequence, the MILP reformulation of Eq.~(\ref{eq:wxconstr}) is marginally
inexact. Despite this issue, the MILP formulation acceptably in practice. \andrea{acceptably what?}}

Substituting the above MILP constraints into the original non-linear
formulation, we obtain the following mixed-integer linear problem:
%
{\footnotesize
\begin{align}
    \max
        & \;\; M - \alpha \sum_{i=1}^k \| \veps^{i} \|_1 - \beta \sum_{i=1}^k \| \vw^{i} \|_1 + \gamma \sum_{i=1}^k \sum_{z=1}^n p^{i,i}_z
        \nonumber
    \\
    \text{s.t.}
        & \;\; \forall \; i \in [k], \forall \; h \in [n] \nonumber
    \\
        & \;\; \qquad \langle \vw^{i}, \vy^{h}_+ - \vy^{h}_- \rangle \ge M - \varepsilon^{i}_h \nonumber
    \\
        & \;\; \forall \; i, j \in [k], i \neq j \;.\; \sum_{z=1}^n p^{i,i}_z - p^{i,j}_z \ge M
    \\
    %     & \;\; \forall \; i \in [k], \forall \; z \in [n] \nonumber
    % \\
        & \;\; \forall \; i, j \in [k], i \neq j, \forall \; z \in [n] \nonumber
    \\
        & \;\; \qquad p^{i,i}_z \le \min \{ w_\text{max} x^{i}_z, w^{i}_z \}
    \\
        & \;\; \qquad p^{i,j}_z \ge \max \{ 0, w^{i}_z - w_\text{max}(1 - x^{j}_z) \}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vw^\bot \le \vw^{i} \le \vw^\top \label{eq:wbounds2}
    \\
        & \;\; \forall \; i \in [k] \;.\; \vx^{i} \in \calX_{\text{feasible}} \nonumber
    \\
        & \;\; \forall \; i \in [k] \;.\; \veps^{i}_h \ge 0 \nonumber
    \\
        & \;\; M \ge 0 \nonumber
\end{align}
}
%
which can be solved by any suitable MILP solver.

\paragraph{Set-wise max-margin.} The full {\sc SetMargin} algorithm
follows the usual preference elicitation loop. Starting from an
initially empty set of user responses $\calD$, it repeatedly solves
the MILP problem above using the set $\calD$ to enforce ranking
constraints on the weight vectors $\{\vw^i\}$. The generated
configurations $\{\vx^i\}$, which are chosen to be as good as possible
with respect to the estimated user preferences, and as diverse as
possible, are then employed to formulate a set of user queries. The
new replies are added to $\calD$ and the whole procedure is
repeated. The algorithm terminates after a fixed number of iterations,
or once another suitable condition is met. \andrea{another suitable
  condition like?}  The procedure is sketched in
Algorithm~\ref{alg:setmargin}. Note that at the end of the preference
elicitation procedure, a final recommendation is made by solving the
MILP problem for $k=1$.

@@

\andrea{questa sezione e' da rivedere, con query selection si itende un'altra cosa di solito}

@@

First, we rewrite the weight vector as $\vw = (\vw_B;\vw_R)$. The utility
becomes:
%
$$ \langle \vw, \vx \rangle = \langle \vw_B, \vx_B \rangle + \langle \vw_R, C \vx_B \rangle = \langle \vw_B + C^\top \vw_B, \vx_B \rangle $$
%
The generalized problem is obtained by substituting $\vw^i$ with $\vv^i := \vw_B^i + C^\top \vv_B^i$ and $p^{i,j}_z$
with $q^{i,j}_z := (\vw^i_B + C^\top \vw^i_R)_z x^j_z$ in the MILP problem.
All constraints remain the same, except Eq.~\ref{eq:wbounds2}, which must be
rewritten in terms of $\vv^i$:
%
$$ \forall \; i \in [k] \;.\; (\vw_B^\bot + C^\bot \vw_R) \le \vv^i \le (\vw_B^\top + C^\top \vw_R^\top)$$
%
As can be seen, non-negativity of $C$ is required for the weights $\{\vv^i\}$
to be non-negative. \andrea{check formulation}
